The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with \textit{Gaia} Data and Beyond

### 2019-05-09 paper/ms.tex
small changes to acknowledgments and my name in the author list

\author[0000-0003-3939-3297]{Robyn Sanderson}
\affil{\cca}
\affil{\penn}

@@

\acknowledgments
We would like to thank Megan Bedell, Robert A. Benjamin, Tobias Buck, Elena
D'Onghia, Benoit Famaey, and Adrian Price-Whelan for helpful discussions. A.B.
would like to thank Todd Phillips for helpful discussions. A.B. was supported
in part by the Roy \& Diana Vagelos Program in the Molecular Life Sciences and
the Roy \& Diana Vagelos Challenge Award. K.V.J.'s and C.F.P.L.'s work was
performed in part during the Gaia19 workshop and the 2019 Santa Barbara Gaia
Sprint (also supported by the Heising-Simons Foundation), both hosted by the
Kavli Institute for Theoretical Physics at the University of California, Santa
Barbara. This work used the Extreme Science and Engineering Discovery
Environment (XSEDE), which is supported by National Science Foundation grant
number OCI-1053575. K.V.J.'s contributions were supported in part by the
National Science Foundation under grants NSF PHY-1748958 and NSF AST-1614743.
M.-M.M.L. was partly supported by NSF grant AST18-15461. The work of D.A.-A.,
A.B., D.W.H., R.S., K.V.J., M.-M.M.L., and M.K.N. is supported by the Simons
Foundation.

>>>>

\author[0000-0003-3939-3297]{Robyn E. Sanderson}
\affil{\cca}
\affil{\penn}

@@

\acknowledgments
We would like to thank Megan Bedell, Robert A. Benjamin, Tobias Buck, Elena
D'Onghia, Benoit Famaey, and Adrian Price-Whelan for helpful discussions. A.B.
would like to thank Todd Phillips for helpful discussions. A.B. was supported
in part by the Roy \& Diana Vagelos Program in the Molecular Life Sciences and
the Roy \& Diana Vagelos Challenge Award. R.E.S's, K.V.J.'s and C.F.P.L.'s work was
performed in part during the Gaia19 workshop and the 2019 Santa Barbara Gaia
Sprint (also supported by the Heising-Simons Foundation), both hosted by the
Kavli Institute for Theoretical Physics at the University of California, Santa
Barbara. This work used the Extreme Science and Engineering Discovery
Environment (XSEDE), which is supported by National Science Foundation grant
number OCI-1053575. K.V.J.'s contributions were supported in part by the
National Science Foundation under grants NSF PHY-1748958 and NSF AST-1614743.
M.-M.M.L. was partly supported by NSF grant AST18-15461. The work of D.A.-A.,
A.B., D.W.H., R.E.S., K.V.J., M.-M.M.L., and M.K.N. is supported by the Simons
Foundation.
